Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-13 tex/paper.tex
added abstract and reformatted

%%%%%%%%% ABSTRACT
\begin{abstract}
   Should we put an abstract here?
\end{abstract}

@@

The rest of this paper is organized as follows.
Section 2 provides an overview of several modern approaches to object recognition
roughly in chronological order, to make it easier to see how strikingly different
solutions to the same problem have evolved.
Section 3 shows how we use ideas from these approaches to design
a convolutional neural network for recognizing hand-written digit data.
Section 4 describes our implementation of a CNN.
Section 5 highlights the performance of our CNN in different conditions and with different depths.
Section 6 concludes with a discussion of the implications of our results, and ideas for
further work.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
   In this paper we describe the design and implementation of a convolutional neural net (a CNN)
   that we use to classify digits from the popular MNIST dataset. We first lay a foundation
   for the merit of convolutional neural nets in object recognition, and then build on this
   foundation to explain our design decisions. The resulting CNN is able to achieve 94\% on the
   MNIST digit dataset while training on only 2\% of the MNIST training set. We feel that the accuracy
   of our CNN could still be improved by training on more images (especially deformed versions of images).
\end{abstract}

@@

The rest of this paper is organized as follows.
Section 2 provides an overview of several modern approaches to object recognition
roughly in chronological order, to make it easier to see how strikingly different
solutions to the same problem have evolved.
Section 3 shows how we use ideas from these approaches to design
a convolutional neural network for recognizing hand-written digit data.
Section 4 highlights the performance of our CNN in different conditions and with different depths.
Section 5 concludes with a discussion of the implications of our results, and ideas for
further work.
